Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-11 scagnostics.Rmd
First attempt at guided tour.

## Smoothness
We first study the smoothness of a subset of measures calculated on a sequence of 2-d projections obtained via an interpolated grand tour path between 4 anchor planes and using the default interpolation angle of 0.05. For this comparison we rescale the data such that each parameter takes values between [0,1]. The temporal trace of a selected set of measures is shown below, where each time step refers to an interpolation step. Note that the value of TIC is strongly dependent on the input distribution and we have therefore rescaled the range for each individual dataset to [0,1], all other measures are reproduced as reported by the calculation.

@@

### Review of guided tour optimisation

### Looking down the pipe
TIC should be able to uncover special view, compare performance of all indices on guided tour path. (also cmass and holes?)

>>>>

## Smoothness
We first study the smoothness of a subset of measures calculated on a sequence of 2-d projections obtained via an interpolated grand tour path between 4 anchor planes and using the default interpolation angle of 0.05. For this comparison we rescale the data such that each parameter takes values between [0,1]. The temporal trace of a selected set of measures is shown below, where each time step refers to an interpolation step. Note that the value of TIC is strongly dependent on the input distribution and we have therefore normalised the TIC measure by its maximum for each individual dataset, all other measures are reproduced as reported by the calculation.

@@

### Review of guided tour optimisation
We use the default method "search_geodesic" implemented in the tourr package. (Should I try other optimisation methods, i.e. search_better, search_better_random?)
Search geodesic first collects $n=5$ samples by default, amongst which the most promising direction is selected. In a second step a linear search along the geodesic is performed in that direction. The optimisation is stopped when ???

### Looking down the pipe
TIC should be able to uncover special view, compare performance of all indices on guided tour path. (also cmass and holes?)
Not currently finding "best" view. Options: compare results from n different random starting planes, try with smaller space (e.g. omitting variable 1 and 2), turn some of the guided tour parameters
```{r findpipe, fig.width=6, fig.height=7, fig.cap="Guided tour optimising TIC index for Pipe 1000 dataset."}
set.seed(2018)
pipeResc <- rescale(pipe1000)
pipeTour <- save_history(pipeResc,
                         guided_tour(mineIndex("TIC")), start = p58)
pipeTourFull <- as.list(interpolate(pipeTour))
pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")
```

```{r testpipe}
iLast <- length(pipeTourFull)
fProj <- pipeTourFull[[iLast]]
dProj <- as.tibble(pipeResc %*% fProj)
ggplot(dProj, aes(V1,V2)) + geom_point()
```
